Streaming Fact Extraction for Wikipedia Entities at Web-Scale

### 2013-11-18 paper/flairs27/content/discussion.tex
Made several changes and clarifications. Removed some authorname information for double blind reviewing
added a comment on the speed of the system

Table~\ref{table:finalresultrecall} shows the distribution of extracted slot names.
The number of extraction between slot names vary greatly.
Some slots naturally have more results than other slots.
For example DateOfDeath and CauseOfDeath have some of the fewest entities because only a few entities are deceased.
Some patterns use common words as as part of their patterns causing more extractions.
For example, Affiliate looks for common words like  \textit{and} and  \textit{with} as part of the pattern content.
These words are more common than \textit{dead}, \textit{died} or \textit{founded} in other patterns.

@@

>>>>

Table~\ref{table:finalresultrecall} shows the distribution of extracted slot names.
The number of extraction between slot names vary greatly.
Some slots naturally have more results than other slots.
For example, DateOfDeath and CauseOfDeath have some of the fewest entities because only a few entities are deceased.
Some patterns use common words as as part of their patterns causing more extractions.
For example, Affiliate looks for common words like  \textit{and} and  \textit{with} as part of the pattern content.
These words are more common than \textit{dead}, \textit{died} or \textit{founded} in other patterns.

@@

The system pipeline architecture is an efficient method of processing the stream of data.
Each hour of in the corpus contains and average of 380 MB of compressed data.
It takes and hour for the system to extract facts from 140 hours worth of data fom the KBA corpus.
